\documentclass[11pt,a4paper,sans]{moderncv} % moderncv package for a more modern look
\moderncvstyle{banking} 
\moderncvcolor{blue} 

\usepackage[scale=0.75]{geometry}

\name{Bryan}{Eaton}
\phone[mobile]{+1-352-578-1242}
\email{bryan.eaton77@gmail.com}
\social[linkedin]{bryanmeaton}

\begin{document}
\makecvtitle

\section{Education}
\cventry{Dec. 2002}{Bachelor of Science in Environmental Science}{Stephen F. Austin State University}{Nacogdoches, TX}{}{}

\section{Experience}
\cventry{Jul 2022 - Present}{Data Engineer}{RegScale, Inc.}{Knoxville, TN}{}{
\begin{itemize}
\item Principal Developer for the RegScale CLI. Led the design and development of core features for this data integration tool, which integrates with over 40 cybersecurity-related services and file-formats.
\item Implemented REST API's and document generation services for OSCAL-compliant XML, FedRAMP, and other formats for the RegScale platform.
\end{itemize}
}
\cventry{Jul 2021 - Jul 2022}{Data Engineer}{Shell Energy}{Remote}{}{
\begin{itemize}
\item Built and maintained pipelines from vendor SQL Server databases to Amazon S3 for user consumption with Dremio and other tools.
\item Wrote the migration code for an Intelometry Retail system (SQL Server based) to an Exelergy RevenueManager data migration using Python, Pytest(Test-Driven Development), SQLAlchemy, Docker, and SQL Server stored procedures/functions.
\end{itemize}
}
\cventry{Oct 2018 - Jul 2021}{Data Engineer}{Oak Ridge National Laboratory}{Remote}{}{
\begin{itemize}
\item Built and maintained pipelines for ingesting millions of JSON documents from multiple sources into an Elasticsearch cluster using Java's Spring Framework and Airflow.
\item Apache ActiveMQ is an open source message broker primarily used for sending messages between applications. Worked on writing message clients for an application centered around JMS messaging.
\end{itemize}
}
\cventry{Jan 2014 - Apr 2018}{SAP Developer}{Oak Ridge National Laboratory}{Remote}{}{
\begin{itemize}
\item Designed focused universes and interactive BI dashboards using SAP Information Design Tool and Design Studio.
\item Used Airflow to extract data from Excel docs with the help of Python Pandas and to integrate this data with parallel Data Services jobs.
\item Setup, schema design and management of Data Marts with SQL Server. SAP Data Services integration for daily ETL ingestion into SQL Server.
\item Wrote Restful API’s using Python’s Flask framework detailing ETL job metrics.  Airflow eventually replaced this setup.
\end{itemize}
}
% Add other experiences in the same way

\section{Programming Skills}
\cvitem{Languages}{Python, Java, Kotlin, GoLang, C$\sharp$, SQL}
\cvitem{Technologies}{Linux, JMS, Flask, Airflow, Vagrant, Docker}

\end{document}
